Update and evaluation of the ozone dry deposition in the OsloCTM3 v1.0

### 2018-12-14 DryDep.tex
Some more polishing of conclusion chapter.

In Eqs.~(\ref{eq:non-stomata-cond}--\ref{eq:SAI}), \citet{ACP:Simpson2012} use prescribed start of growing season (SGS) and end of growing season (EGS) at $50\,\unit{^\circ N}$ ($d_\text{SGS}$, $d_\text{EGS}$) together with leaprates ($\nabla d_\text{SGS}$, and $\nabla d_\text{EGS}$) to define phenology and dry deposition over agricultural areas. For the growing season of crops in the computation of non-stomatal conductances, we use also prescribed values (Table~\ref{tab:growing_season}), while for the stomatal conductances, as shown in Eq.~(\ref{eq:fphen}), we use the SGS and EGS derived parameters: day of greening season (GDAY), the time elapsed starting at the SGS, and the total length of the greening season (GLEN), the time span between EGS and SGS. Since the eurocentric EMEP parameterization of SGS and EGS is not applicable in a global model, another latitude dependent parameterization is needed. First, we have used a parameterization as implemented in the Sparse Matrix Operational Kernel Emissions -- Biogenic Emission Inventory System (SMOKE-BEIS; \href{https://www.epa.gov/air-emissions-modeling/biogenic-emission-inventory-system-beis}{model webpage}). SMOKE-BEIS has fixed values for SGS and EGS for all regions but NH mid latitudes ($23\,\unit{^\circ} < \text{lat} < 65\,\unit{^\circ}$), where it uses leaprates of $\nabla d_\text{SGS} = 4.5$ and $\nabla d_\text{EGS} = 3.3$. As this parameterization is optimized for North America, it does not work well in Europe, e.g., most of northern Scandinavia has no allocated vegetation period.\\

In agriculture, there are different empirical rules to estimate the SGS and EGS. The simplest assumption is that greening starts after five consecutive days with a daily average temperature above $5\,\unit{^\circ C}$ and vice versa for EGS. Other estimates use growing degree days \citep{JC:Levis2004,PO:Fu2014}, include soil moisture \citep{GCB:Fu2014}, or rely on satellite observations. A comprehensive evaluation of different tecniques is given by \citet{GCB:Anav2017}.

@@

As dry deposition velocities are not directly available from the model output, monthly average dry deposition velocities $v^\chem{O_3}_\text{DD}$ have been reconstructed from the ratio between the total ozone dry deposition $\sum \chem{O_3^\text{DD}}(z_0)$ and monthly averaged surface ozone amount $\chem{O_3}(z_0)$ 
\begin{equation}
  v^\chem{O_3}_\text{DD} = \frac{\sum \chem{O_3^\text{DD}}(z_0)}{\chem{O_3}(z_0)}\cdot c_\text{month}.
\end{equation}
Herein $c_\text{month} = \frac{\Delta h_\text{month}}{s_\text{month}}$ with the average height of the lowermost model level in each gridbox $\Delta h_\text{month}$, which is changing with temperature and surface pressure, and the respective number of seconds in a month $s_\text{month}$.
%
\subsubsection{Zonal distribution}
\label{subsubsec:zonal}
%
The annual zonal average with respect to surface ozone concentration (Fig.~\ref{fig:mmm_drydep}a) displays, in consistency with Fig.~\ref{fig:diff_maps}a), a general, global increase of ozone by up to $10\,\unit{ppb}$. This increase is largest in the zonal band $(25-50)\,\unit{^\circ N}$ which contains the major deserts. In the deep tropics ($5\,\unit{^\circ S}-5\,\unit{^\circ N}$), the increase is smallest ($\Delta[\chem{O_3}]\leq 5\,\unit{ppb}$). We find that the EMEP scheme further intensifies the strong asymmetry between northern and southern hemisphere as a consequence of the distribution of the continental land masses and vegetation thereon. Among the sensitivity studies, there is only a low absolute variance. Most remarkable but expected due to the much smaller prescribed dry deposition velocity over ice and snow, \emph{EMEP\_ppgssh\_ice} displays almost a doubling of surface ozone in the high Arctics compared to \emph{Wesely\_type} but affects ozone concentrations down to latitudes at about $50\,\unit{^\circ}$ in both hemispheres. Neglecting any dependence on solar radiation in the stomatal conductance formulation (\emph{EMEP\_offLight}) -- or in other words allowing photosynthesis 24/7 -- generally decreases the ozone concentration by about $2\,\unit{ppb}$, while choosing soil water at deeper levels than the surface layer (\emph{EMEP\_SWVL4}) increases $[\chem{O_3}](z_0)$ slightly. Rather surprisingly, switching off the phenology completely (\emph{EMEP\_offPhen}), amounts only to small difference (at most $3.5\,\unit{\%}$ increase in the deep tropics). Switching from the SMOKE-BEIS parameterization to the pre-processed greening season (\emph{EMEP\_ppgs} compared to \emph{EMEP\_full}), surface ozone increases on average by $6\,\unit{\%}$ between $(54-70)\,\unit{^\circ N}$. The scenario of differing emissions (2005 in comparison to 2014 or more specifically \emph{EMEP\_ppgs\_2005} compared to \emph{EMEP\_ppgs}), yields higher ozone concentrations in the northern hemisphere in 2005 in accordance to a reduction in sulfur and \chem{NO_x} emissions in south east Asia in later years. An opposite tendency is seen for latitudes south of $30\,\unit{^\circ N}$, probably owing to the industrial development of countries in these regions.

@@

There seems to be a discrepancy between the OsloCTM3 response and the multi-model-mean, since the Wesely scheme is closer to the multi-model-mean with respect to total annual ozone dry deposition, while the reconstructed $v_\text{DD}^\chem{O_3}$ of the EMEP scheme match better. Without knowing the actual $[\chem{O_3}(z_0)]$ of the TF~HTAP models that participated in the model intercomparison, we cannot elaborate on this discrepancy.

@@

In Fig.~\ref{fig:mmm_drydep_season_pft}, the seasonal cycles of dry deposition velocities are shown for the nine surface categories. The patterns and absolute numbers differ substantially between the Wesely scheme and the EMEP scheme and the multi-model-mean. The divergence of the average dry deposition velocities between the Wesely scheme and the EMEP scheme in desert regions ($\Delta \overline{v}_\text{desert}^\chem{O_3} = 0.18\,\unit{cm\,s^{-1}}$) as well as grassland ($\Delta \overline{v}_\text{grassland}^\chem{O_3} = 0.54\,\unit{cm\,s^{-1}}$) is quite remarkable as well as the difference of both to the multi-model-mean in tropical forest regions ($\Delta \overline{v}_\text{tropical forest}^\chem{O_3} = 0.49\,\unit{cm\,s^{-1}}$). In contrast to the Wesely scheme and the EMEP scheme, the multi-model-mean indicates a rather pronounced seasonal cycle in desert regions ($0.10\,\unit{cm\,s^{-1}} \leq v^\chem{O_3}_\text{desert}\leq 0.15\,\unit{cm\,s^{-1}}$). The estimated dry deposition velocities over desert regions are consistent with the previously mentioned baseline values of ozone dry deposition, which means that in the EMEP scheme they are about one order of magnitude lower than in the Wesely scheme. From measurements of ozone fluxes in the Sahara desert, \citet{AE:Gusten1995} deduced $v^\chem{O_3}_\text{desert, day} = 0.1\,\unit{cm\,s^{-1}}$, $v^\chem{O_3}_\text{desert, night} = 0.04\,\unit{cm\,s^{-1}}$, and $\overline{v}^\chem{O_3}_\text{desert} = 0.065\,\unit{cm\,s^{-1}}$. This implies, that ozone dry deposition over desert regions is highly overestimated in the Wesely scheme as well as in TF~HTAP models, while it may be underestimated in the EMEP scheme. Similarly, the dry deposition velocities over water differ. From measurements over the ocean a mean value of $\overline{v}^\chem{O_3}_\text{water} = 0.019\,\unit{cm\,s^{-1}}$ has been deduced \citep{JGR:Helmig2012}. In a model study of different mechanisms of dry deposition to ocean waters by means of prescribed $\overline{v}_\text{water}^\chem{O_3}$ and one- and two-layer gas exchange modeling, \citet{ACP:Luhar2017} found $\overline{v}_\text{water}^\chem{O_3}$ ranging between $0.018\,\unit{cm\,s^{-1}}$ (two-layer scheme) and $0.039\,\unit{cm\,s^{-1}}$ (prescribed). With $\overline{v}^\chem{O_3}_\text{water} = (0.046\pm0.002)\,\unit{cm\,s^{-1}}$, the EMEP scheme (Section~\ref{subsubsec:Rb}) yields probably a too strong dry deposition to ocean which implies that ozone concentrations might even become larger and dry deposition even lower in the model if a two-layer scheme would be implemented. With respect to vegetation, we might be able to improve the model performance further by allowing more PFTs and phenologies, especially in regions covered by tropical or coniferous forest \citep{GCB:Anav2017}. 

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conclusions[Discussion and conclusions]  %% \conclusions[modified heading if necessary]
\label{sec:conc}
We have presented an update of the dry deposition scheme in the OsloCTM3 from prescribed dry deposition velocities \citep{AE:Wesely1989,JGR:Hough1991} to a more process-oriented parameterization taking the state of the atmosphere and vegetation into account \citep{ACP:Simpson2012}. The dry deposition to vegetation is now sensitive to parameters such as photosynthetic active radiation, water vapor pressure deficit, soil water content, and plant phenology. Due to changes in dry deposition velocities $v_\text{DD}^\chem{O_3}$, the annual amount of ozone dry deposition decreases by up to $100\,\unit{\%}$ especially over large desert regions and the oceans. Compared to results from a multi-model evaluation \citep{ACP:Hardacre2015}, the total annual ozone dry deposition in the OsloCTM3 is about $33\,\unit{\%}$ below the average. However, there seems to be a tendency, that the newer TF~HTAP models show a lower total annual dry deposition of ozone than older models, indicating that newer developments in the models lead to decreasing ozone dry deposition and increasing tropospheric ozone burden \citep[e.g.,][]{ACP:Luhar2017,AE:Hu2017}. We found the response of the OsloCTM3 to the changes in dry deposition velocities consistent between the old and the new dry deposition scheme. A decrease in $v_\text{DD}^\chem{O_3}$ leads to a decrease in total ozone dry deposition and an increase in surface ozone concentration $[\chem{O_3}(z_0)]$. However, there is an apparent discrepancy when comparing with the multi-model-mean. Without knowing $[\chem{O_3}(z_0)]$ of the TF~HTAP models, this cannot be resolved.

Most of the decrease in ozone dry deposition in the OsloCTM3 is due to changes in dry deposition velocities over the ocean and deserts. In case of desert and grasslands this change is at the order of one magnitude. Over the ocean it is due to the accumulative effect of a small absolute change in dry deposition which is especially amplified in the southern hemisphere. With respect to available measurements of dry deposition velocities of ozone over desert \citep{AE:Gusten1995} and ocean \citep{JGR:Helmig2012}, the new OsloCTM3 dry deposition scheme slightly underestimates ozone dry deposition velocities over the former and overestimate them over the latter. Regarding the vastness of the ocean and the ongoing desertification, it may be worthwhile to study dry deposition in these regimes at a more process-oriented level, e.g., 2-layer gas exchange with ocean waters \citep{ACP:Luhar2017}, wave braking and spray \citep{ACP:Pozzer2006}.

@@

We have studied the parameter space of the stomatal conductance parameterization and found that total surface ozone in the tropics is most sensitive to changes in ozone uptake by plants. This may indicate that future changes in vegetation cover and solar radiation at the surface due to changes in stratospheric ozone, cloud cover, or aerosols could also strongly influence the surface ozone burden in the tropics. Total column ozone in the tropics is predicted to decrease due to changes in the atmospheric circulation \citep[e.g.,][]{WMO2014}, while tropospheric and surface ozone increase. The combined effects of increasing emissions of ozone precursors and an increase in UV due to thinning of stratospheric ozone might permit more UV light at ground and thus increase the ozone production.

>>>>

In Eqs.~(\ref{eq:non-stomata-cond}--\ref{eq:SAI}), \citet{ACP:Simpson2012} use prescribed start of growing season (SGS) and end of growing season (EGS) at $50\,\unit{^\circ N}$ ($d_\text{SGS}$, $d_\text{EGS}$) together with lapse rates ($\nabla d_\text{SGS}$, and $\nabla d_\text{EGS}$) to define phenology and dry deposition over agricultural areas. For the growing season of crops in the computation of non-stomatal conductances, we use also prescribed values (Table~\ref{tab:growing_season}), while for the stomatal conductances, as shown in Eq.~(\ref{eq:fphen}), we use the SGS and EGS derived parameters: day of greening season (GDAY), the time elapsed starting at the SGS, and the total length of the greening season (GLEN), the time span between EGS and SGS. Since the eurocentric EMEP parameterization of SGS and EGS is not applicable in a global model, another latitude dependent parameterization is needed. First, we have used a parameterization as implemented in the Sparse Matrix Operational Kernel Emissions -- Biogenic Emission Inventory System (SMOKE-BEIS; \href{https://www.epa.gov/air-emissions-modeling/biogenic-emission-inventory-system-beis}{model webpage}). SMOKE-BEIS has fixed values for SGS and EGS for all regions but NH mid latitudes ($23\,\unit{^\circ} < \text{lat} < 65\,\unit{^\circ}$), where it uses lapse rates of $\nabla d_\text{SGS} = 4.5$ and $\nabla d_\text{EGS} = 3.3$. As this parameterization is optimized for North America, it does not work well in Europe, e.g., most of northern Scandinavia has no allocated vegetation period.\\

In agriculture, there are different empirical rules to estimate the SGS and EGS. The simplest assumption is that greening starts after five consecutive days with a daily average temperature above $5\,\unit{^\circ C}$ and vice versa for EGS. Other estimates use growing degree days \citep{JC:Levis2004,PO:Fu2014}, include soil moisture \citep{GCB:Fu2014}, or rely on satellite observations. A comprehensive evaluation of different techniques is given by \citet{GCB:Anav2017}.

@@

As dry deposition velocities are not directly available from the model output, monthly average dry deposition velocities $v^\chem{O_3}_\text{DD}$ have been reconstructed from the ratio between the total ozone dry deposition $\sum \chem{O_3^\text{DD}}(z_0)$ and monthly averaged surface ozone amount $\chem{O_3}(z_0)$ 
\begin{equation}
  v^\chem{O_3}_\text{DD} = \frac{\sum \chem{O_3^\text{DD}}(z_0)}{\chem{O_3}(z_0)}\cdot c_\text{month}.
\end{equation}
Herein $c_\text{month} = \frac{\Delta h_\text{month}}{s_\text{month}}$ with the monthly average height of the lowermost model level in each gridbox $\Delta h_\text{month}$ and the respective number of seconds in a month $s_\text{month}$.
%
\subsubsection{Zonal distribution}
\label{subsubsec:zonal}
%
The annual zonal average with respect to surface ozone concentration (Fig.~\ref{fig:mmm_drydep}a) displays on average, in consistency with Fig.~\ref{fig:diff_maps}a), a global increase of surface ozone concentrations by up to $10\,\unit{ppb}$ applying the EMEP scheme compared to the Wesely scheme. This increase is largest in the zonal band $(25-50)\,\unit{^\circ N}$ which contains the major deserts. In the deep tropics ($5\,\unit{^\circ S}-5\,\unit{^\circ N}$), the increase is smallest ($\Delta[\chem{O_3}]\leq 5\,\unit{ppb}$). We find that the EMEP scheme further intensifies the strong asymmetry between northern and southern hemisphere as a consequence of the distribution of the continental land masses and vegetation thereon. Among the sensitivity studies, there is only a low absolute variance. Most remarkable but expected due to the much smaller prescribed dry deposition velocity over ice and snow, \emph{EMEP\_ppgssh\_ice} displays almost a doubling of surface ozone in the high Arctics compared to \emph{Wesely\_type} but affects ozone concentrations down to latitudes at about $50\,\unit{^\circ}$ in both hemispheres. Neglecting any dependence on solar radiation in the stomatal conductance formulation (\emph{EMEP\_offLight}) -- or in other words allowing photosynthesis 24/7 -- generally decreases the ozone concentration by about $2\,\unit{ppb}$, while choosing soil water at deeper levels than the surface layer (\emph{EMEP\_SWVL4}) increases $[\chem{O_3}](z_0)$ slightly. Rather surprisingly, switching off the phenology completely (\emph{EMEP\_offPhen}), amounts only to small difference (at most $3.5\,\unit{\%}$ increase in the deep tropics). Switching from the SMOKE-BEIS parameterization to the pre-processed greening season (\emph{EMEP\_ppgs} compared to \emph{EMEP\_full}), surface ozone increases on average by $6\,\unit{\%}$ between $(54-70)\,\unit{^\circ N}$. The scenario of differing emissions (2005 in comparison to 2014 or more specifically \emph{EMEP\_ppgs\_2005} compared to \emph{EMEP\_ppgs}), yields higher ozone concentrations in the northern hemisphere in 2005 in accordance to a reduction in sulfur and \chem{NO_x} emissions in south east Asia in later years. An opposite tendency is seen for latitudes south of $30\,\unit{^\circ N}$, probably owing to the industrial development of countries in these regions.

@@

There seems to be a discrepancy between the OsloCTM3 response and the multi-model-mean, since the Wesely scheme is similar to the multi-model-mean with respect to total annual ozone dry deposition, while the reconstructed $v_\text{DD}^\chem{O_3}$ of the EMEP scheme match better. This could be a sign of differences in photo-chemistry and transport (e.g. convective, advective, STE) between the OsloCTM3 and the average TF~HTAP model, but without looking at the actual $[\chem{O_3}(z_0)]$ of the TF~HTAP models that participated in the model intercomparison, we cannot elaborate on this any further.

@@

In Fig.~\ref{fig:mmm_drydep_season_pft}, the seasonal cycles of dry deposition velocities are shown for the nine surface categories. The patterns and absolute numbers differ substantially between the Wesely scheme and the EMEP scheme and the multi-model-mean. The divergence of the average dry deposition velocities between the Wesely scheme and the EMEP scheme in desert regions ($\Delta \overline{v}_\text{desert}^\chem{O_3} = 0.18\,\unit{cm\,s^{-1}}$) as well as grassland ($\Delta \overline{v}_\text{grassland}^\chem{O_3} = 0.54\,\unit{cm\,s^{-1}}$) is quite remarkable as well as the difference of both to the multi-model-mean in tropical forest regions ($\Delta \overline{v}_\text{tropical forest}^\chem{O_3} = 0.49\,\unit{cm\,s^{-1}}$). In contrast to the Wesely scheme and the EMEP scheme, the multi-model-mean indicates a rather pronounced seasonal cycle in desert regions ($0.10\,\unit{cm\,s^{-1}} \leq v^\chem{O_3}_\text{desert}\leq 0.15\,\unit{cm\,s^{-1}}$). The estimated dry deposition velocities over desert regions are consistent with the previously mentioned baseline values of ozone dry deposition, which means that in the EMEP scheme they are about one order of magnitude lower than in the Wesely scheme. From a limited number of ozone flux measurements in the Sahara desert, \citet{AE:Gusten1995} deduced $v^\chem{O_3}_\text{desert, day} = 0.1\,\unit{cm\,s^{-1}}$, $v^\chem{O_3}_\text{desert, night} = 0.04\,\unit{cm\,s^{-1}}$, and $\overline{v}^\chem{O_3}_\text{desert} = 0.065\,\unit{cm\,s^{-1}}$. This implies, that ozone dry deposition over desert regions is highly overestimated in the Wesely scheme as well as in TF~HTAP models, while it may be underestimated in the EMEP scheme. Similarly, the dry deposition velocities over water differ. From measurements during ship-campaigns a mean value of $\overline{v}^\chem{O_3}_\text{water} = 0.019\,\unit{cm\,s^{-1}}$ over the ocean has been deduced \citep{JGR:Helmig2012}. In a model study of different mechanisms of dry deposition to ocean waters by means of prescribed $\overline{v}_\text{water}^\chem{O_3}$ and one- and two-layer gas exchange modeling, \citet{ACP:Luhar2017} found $\overline{v}_\text{water}^\chem{O_3}$ ranging between $0.018\,\unit{cm\,s^{-1}}$ (two-layer scheme) and $0.039\,\unit{cm\,s^{-1}}$ (prescribed). With $\overline{v}^\chem{O_3}_\text{water} = (0.046\pm0.002)\,\unit{cm\,s^{-1}}$, the EMEP scheme (Section~\ref{subsubsec:Rb}) yields probably a too strong dry deposition to ocean which implies that ozone concentrations might even become larger and dry deposition even lower in the model if a two-layer scheme would be implemented. With respect to vegetation, we might be able to improve the model performance further by allowing more PFTs and phenologies, especially in regions covered by tropical or coniferous forest \citep{GCB:Anav2017}. 

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conclusions[Discussion and conclusions]  %% \conclusions[modified heading if necessary]
\label{sec:conc}
We have presented an update of the dry deposition scheme in the OsloCTM3 from purely prescribed dry deposition velocities \citep{AE:Wesely1989,JGR:Hough1991} to a more process-oriented parameterization taking the state of the atmosphere and vegetation into account \citep{ACP:Simpson2012}. In our implementation based on \citet{ACP:Simpson2012}, we follow a classical, resistance analogous approach in computing contributions to dry deposition. The quasi-laminar resistance in the dry deposition scheme is capable of adjusting to surface wind stress but falls back to its prescribed limits in most of the tested cases. The surface resistance computation is divided into stomatal and non-stomatal resistance. The stomatal resistance is sensitive to parameters associated with the state of vegetation such as photosynthetic active radiation, water vapor pressure deficit, soil water content, and plant phenology, while the non-stomatal resistance is affected by the existence or absence of vegetation.

The annual amount of ozone dry deposition decreases by up to $100\,\unit{\%}$ changing from the old dry deposition scheme to the new one. Compared to results from a multi-model evaluation \citep{ACP:Hardacre2015}, the total annual ozone dry deposition in the OsloCTM3 is about $33\,\unit{\%}$ below average. However, there seems to be a tendency, that newer TF~HTAP models show a lower total annual dry deposition of ozone than older models, indicating that newer developments lead to decreasing ozone dry deposition and increasing tropospheric ozone burden \citep[e.g.,][]{ACP:Luhar2017,AE:Hu2017}.

We found the response of the OsloCTM3 to the changes in dry deposition velocities from the old and the new dry deposition scheme to be consistent. A decrease in $v_\text{DD}^\chem{O_3}$ leads to a decrease in total ozone dry deposition and an increase in surface ozone concentration $[\chem{O_3}(z_0)]$. As the new scheme is more similar to the multi-model-mean \citep{ACP:Hardacre2015} with respect to dry deposition velocities, while the old scheme agrees better in terms of total dry deposition, there is an apparent discrepancy when comparing with the multi-model-mean. Without knowing $[\chem{O_3}(z_0)]$ of the TF~HTAP models, this cannot be resolved and may even hint to differences in photo-chemistry as well as stratosphere-troposphere-exchange.

Most of the decrease in ozone dry deposition in the OsloCTM3 can be attributed to changes in dry deposition velocities over the ocean and deserts. This is mainly due to updates of the respective prescribed dry deposition velocities $v_\text{DD}^\chem{O_3}$. In case of desert and grasslands the difference between the old and new prescribed value is at the order of one magnitude. Over the ocean, the absolute change in dry deposition is small, but it is accumulated over a large area which is especially amplified in the southern hemisphere. With respect to available measurements of dry deposition velocities of ozone over desert \citep{AE:Gusten1995} and ocean \citep{JGR:Helmig2012}, the new OsloCTM3 dry deposition scheme slightly underestimates ozone dry deposition velocities over the former and overestimate them over the latter. Regarding the vastness of the ocean and the ongoing desertification, it may be worthwhile to study dry deposition in these regimes at a more process-oriented level, e.g., 2-layer gas exchange with ocean waters \citep{ACP:Luhar2017}, wave braking and spray \citep{ACP:Pozzer2006}.

@@

We have studied the parameter space of the stomatal conductance parameterization and found that total surface ozone in the tropics is most sensitive to changes in ozone uptake by plants. The difference between our most extreme test cases amounts to $15\,\unit{\%}$with respect to total surface ozone, while the more realistic test case using differing years of emission amounts to about $5\,\unit{\%}$. This may indicate that future changes in vegetation cover and solar radiation at the surface due to changes in stratospheric ozone, cloud cover, or aerosols could also strongly influence the surface ozone burden in the tropics. Total column ozone in the tropics is predicted to decrease due to changes in the atmospheric circulation \citep[e.g.,][]{WMO2014}, while tropospheric and surface ozone increase. The combined effects of increasing emissions of ozone precursors and an increase in UV due to thinning of stratospheric ozone might permit more UV light at ground and thus increase the ozone production.
